\documentclass[conference]{IEEEtran}

% --- Packages ----------------------------------------------------------------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{cite}
\usepackage{listings}
\usepackage{xcolor}

% --- Code listing style ------------------------------------------------------
\definecolor{lightgray}{rgb}{0.95,0.95,0.95}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}

\lstset{
  basicstyle=\ttfamily\footnotesize,
  breaklines=true,
  frame=single,
  backgroundcolor=\color{lightgray},
  keywordstyle=\color{blue},
  commentstyle=\color{darkgreen},
}

% --- Title and Authors -------------------------------------------------------
\title{Adaptive Cruise Controller for RC Car Using STM32}

\author{
  \IEEEauthorblockN{Erickson A.\ Mijangos}
  \IEEEauthorblockA{Department of Electrical Engineering\\
  University Name, City, State\\
  email@university.edu}
  \and
  \IEEEauthorblockN{Dr.\ Mike Turi}
  \IEEEauthorblockA{Department of Electrical Engineering\\
  University Name, City, State\\
  email@university.edu}
}

% =============================================================================
\begin{document}

\maketitle

% --- Abstract ----------------------------------------------------------------
\begin{abstract}
Write your abstract here. Summarize the system, methods, and key results
in 150--250 words.
\end{abstract}

\begin{IEEEkeywords}
Adaptive Cruise Control, STM32, PID Controller, LIDAR, NRF24L01, PyQt5, UART.
\end{IEEEkeywords}

% --- I. Introduction ---------------------------------------------------------
\section{Introduction}
\label{sec:intro}

Your introduction goes here. Hi my namer Mango.

% --- II. Hardware Architecture -----------------------------------------------
\section{Hardware Architecture}
\label{sec:hardware}

Your hardware section goes here.

\subsection{RC Car Node}

Subsection content.

\subsection{Transmitter Node}

Subsection content.

% --- III. Firmware Design ----------------------------------------------------
\section{Firmware Design}
\label{sec:firmware}

Your firmware section goes here.

% --- IV. Python GUI ----------------------------------------------------------
\section{Python Graphical User Interface}
\label{sec:software}

Your GUI section goes here.

% --- V. Results --------------------------------------------------------------
\section{Experimental Results}
\label{sec:results}

Your results go here.

% --- VI. Conclusion ----------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

Your conclusion goes here.

% --- References --------------------------------------------------------------
\begin{thebibliography}{9}

\bibitem{stm32h723}
STMicroelectronics, \textit{STM32H723ZG Datasheet}, Rev.~4, 2022.

\bibitem{lidar}
Garmin Ltd., \textit{LIDAR-Lite v3 Operation Manual}, 2017.

\end{thebibliography}

\end{document}
